---
title: "PSY4960_StepF"
author: "Yangchenchen Liu"
date: "2022-12-03"
output: html_document
---

1 Data Import
```{r}
UROP2018Dat <- read.csv("UROP2018Dat.csv")
summary(UROP2018Dat)
```

2 Data Clean
```{r}
# depressFrequency: categorical variable to numeric variable
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="总是"] <- 5
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="经常"] <- 4
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="有时"] <- 3
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="很少"] <- 2
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="从不"] <- 1
UROP2018Dat$depressFrequency[UROP2018Dat$depressFrequency=="拒绝回答"] <- NA

# SWB: categorical variable to numeric variable
UROP2018Dat$SWB[UROP2018Dat$SWB=="非常不幸福"] <- 1
UROP2018Dat$SWB[UROP2018Dat$SWB=="比较不幸福"] <- 2
UROP2018Dat$SWB[UROP2018Dat$SWB=="说不上幸福不幸福"] <- 3
UROP2018Dat$SWB[UROP2018Dat$SWB=="比较幸福"] <- 4
UROP2018Dat$SWB[UROP2018Dat$SWB=="非常幸福"] <- 5
UROP2018Dat$SWB[UROP2018Dat$SWB=="拒绝回答"] <- NA

#gender: categorical variable to dummy/binary variable
UROP2018Dat$gender[UROP2018Dat$gender=="女"] <- 0
UROP2018Dat$gender[UROP2018Dat$gender=="男"] <- 1

#character to numeric 
UROP2018Dat$depressFrequency <- as.numeric(UROP2018Dat$depressFrequency)
UROP2018Dat$SWB <- as.numeric(UROP2018Dat$SWB)
UROP2018Dat$gender <- as.numeric(UROP2018Dat$gender)
summary(UROP2018Dat)
```

3. Data Analysis
```{r}
# depressFrequency Table
table(UROP2018Dat$depressFrequency)
```

```{r}
# SWB Table
table(UROP2018Dat$SWB)
```

```{r}
# summary Age
summary(UROP2018Dat$age)
```

H1: As people's age increases, their subjective well-being will increase. 
```{r}
# Linear Regression
linearRegression2018_1 <- lm(SWB~age, data=UROP2018Dat)
summary(linearRegression2018_1)
```

H2: As people's age increases, their frequency of having depressive mood will increase. 
```{r}
linearRegression2018_2 <- lm(depressFrequency~age, data=UROP2018Dat)
summary(linearRegression2018_2)
```

H3: People who have higher SWB will have a smaller frequency of feeling depressed
```{r}
cor.test(UROP2018Dat$depressFrequency, UROP2018Dat$SWB)
```

4. Virtual Analysis

H1: As people's age increases, their subjective well-being will increase. 

Figure 1: Regression line of mean SWB by Age group
```{r}
library(ggplot2)
meanSWBbyAge2018<- aggregate(as.numeric(UROP2018Dat$SWB), list(UROP2018Dat$age), FUN=mean, na.rm=T)

ggplot(meanSWBbyAge2018, aes(Group.1, x)) + geom_point(color="orange") + xlab("Age") +ylab("Subjective Well-being Mean of the Age") +theme_classic() +ggtitle("2018 Chinese Adults' Subjective Well-being Mean by Age") + geom_smooth(method="lm", color="orange", se=FALSE)
```

H2: As people's age increases, their frequency of having depressive mood will increase. 

Figure 2: Regression line of mean Depress Frequency by Age group
```{r}
meandepressFrequencybyAge2018<- aggregate(as.numeric(UROP2018Dat$depressFrequency), list(UROP2018Dat$age), FUN=mean, na.rm=T)

ggplot(meandepressFrequencybyAge2018, aes(Group.1, x)) + geom_point(color="orange") + xlab("Age") +ylab("Depress Frequency Mean of the Age") +theme_classic() +ggtitle("2018 Chinese Young Adults' Depress Frequency Mean by Age") + geom_smooth(method="lm", color="orange", se=FALSE)
```

H3: People who have higher SWB will have a smaller frequency of feeling depressed

Figure 3: Histogram of SWB
```{r}
ggplot(UROP2018Dat, aes(SWB)) + geom_histogram(color="orange", fill="yellow") + theme_classic() +ggtitle ("Histogram of 2018 Chinese Young Adults' SWB") 
```

Figure 4: Histogram of Frequency of Depressive Mood
```{r}
ggplot(UROP2018Dat, aes(depressFrequency)) + geom_histogram(color="orange", fill="yellow") + theme_classic() +ggtitle ("Histogram of 2018 Chinese Young Adults' Frequency of Depressive Mood") 
```
